Viscous Transport in Eroding Porous Media

### 2019-08-29 docs/transport/erosion_transport.tex
small changes to section 6.3

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.7\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.7\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The flow
rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded. \todo[inline]{S-H:
Let's bring the black dashed line closer to the blue line}}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.  Each body is discretized with $N_\iin =
256$, and the smallest distance between two bodies at the initial
condition is $3.29 \times 10^{-4}$.  At this resolution, this
corresponds to a spacing of $0.0471h$ which is too small for the
trapezoid rule to guarantee a sufficiently small quadrature error.  By
applying the Barycentric quadrature rule, there is no issue simulating
the erosion until all the bodies have eroded.

>>>>

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.7\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[height = 0.7\linewidth]{./figs/flow_rate20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The flow
rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Low Porosity}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider a second example with 20 eroding bodies, but with a smaller
initial porosity.  In Figure~\ref{fig:ErodingLow20vort}, we plot the
eroding geometry and porosity at four evenly spaced instances in time.
Again, the color is the vorticity in the bulk whose magnitude is
equivalent to the erosion rate.   Initially, the smallest distance
between pairs of bodies is $3.29 \times 10^{-4}$, and the smallest
distance between the bodies and solid wall is $4.50 \times 10^{-3}$.  At
these distances, a resolution of approximately $N_\iin = 27,000$ and
$N_\out = 18,000$ discretization points is required to satisfy the $5h$
rule of thumb that is required for the trapezoid rule to achieve machine
epsilon accuracy.  By applying the Barycentric quadrature rule, we
stably simulate erosion at the much coarser resolution of $N_\iin = 256$
and $N_\out = 1024$ discretization points.
